Biden Projected to Win in the 2024 US Presidential Election

### 2024-03-15 paper/paper.qmd
added the discussion section

The paper is further organised into three sections: Data, Model, Results, and Discussion. In the Data section, we discuss how the datasets to be used for the analysis were obtained and pre-processed. We will explain the variables of interest in the datasets for the analysis. The Model section describes the model being used for the analyis. The Results section will then highlight and discuss the trends and associations found during the analysis. Lastly, the Discussion section will talk about some interesting trends found in Results in depth, link it to the real world and also highlight the weaknesses of our analysis.

@@

##Introduction to the Data:
We will use the most recent American Community Survey, the 2022 Sample, as the post-stratification dataset
to represent the voter population and adjust the weight of the survey data. The population for this sample was the entire US population, categorized into households as subgroups, and the responses of the sampled subgroups were collected. ACS 2022 dataset consists of 3,373,378 observations.

@@

## Weaknesses and Limitations: (Need to edit this)

>>>>

The paper is further organised into four sections: Data, Model, Results, and Discussion. In the Data section,
 discuss how the datasets to be used for the analysis were obtained and pre-processed. We will explain the variables of interest in the datasets for the analysis. The Model section describes the model being used for the analyis. The Results section will then highlight and discuss the trends and associations found during the analysis. Lastly, the Discussion section will talk about some interesting trends found in Results in depth, link it to the real world and also highlight the weaknesses of our analysis.

@@

## Introduction to the Data:

We will use the most recent American Community Survey, the 2022 Sample, as the post-stratification dataset
to represent the voter population and adjust the weight of the survey data. The population for this sample was the
entire US population, categorized into households as subgroups, and the responses of the sampled subgroups were collected.
ACS 2022 dataset consists of 3,373,378 observations.

@@

## Weaknesses and Limitations:
